\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{Carter Rhea}
\title{Math 295: Homework 9}
\begin{document}
\maketitle
\begin{enumerate}
\item Chapter 5.2 $\#$ 3 Which of the functions in exercise 3 of $\S$ 5.1 are one-to-one and which are onto?\\
\begin{enumerate}
\item Let $A=\{a,b,c,\}$ and $B=\{a,b\}$, and $\{(a,b),(b,b),(c,a)\}$.\\
$f$ is not one-to-one but it is onto.
\item Let $f : \mathbb{R} \to \mathbb{R}$ be the function defined by the formula $f(x)= x^2 - 2x$.\\
$f$ is both one-to-one and onto.
\item Let $f= \{(x,n) \in \mathbb{R} \times \mathbb{Z} | n \leq x < n+1 \}$.\\
\end{enumerate}
\item Chapter 5.2 \#6 Let $A = \mathcal{P}(\mathbb{R})$. Define $f : \mathbb{R} \to A$ by the formula $f(x) = \{y \in \mathbb{R} | y^2 <x  \}.$
\begin{enumerate}
\item Find $f(2)$.\\
$f(2) = y< \sqrt[2]{2}$
\item Is $f$ one-to-one? Is it onto?\\
$f$ is one-to-one, but $f$ is not onto.
\end{enumerate}
\item Chapter 5.2 \# 8 Suppose $f : A \to B$ and $g : B \to C$. 
\begin{enumerate}
\item Prove that if $g \circ f$ is onto then $g$ is onto.\\
Proof: Assume $(g \circ f)(x)$ is onto. Thus, by the definition of compisition of $g(f(x))$. Since, $g(f(x))$ is onto, there exists some $a \in A$ such that $g(f(x))=c$ such that $c \in C$. Since $a,c$ were arbitrary, we can find an $a \in A$ , such that $g(f(x)) =c$. Thus $g(f(x))=(g \circ f)(x)$ is onto.
\item Prove that if $g \circ f$ is one-to-one then $f$ is onto.\\
Proof: Assume $(g \circ f)(x)$ is one-to-one. Thus $g(f(x))$ is one-to-one. Given $a_1 , a_2 \in A$, by the definition of one-to-one $g(f(a_1))=g(f(a_2)) \to a_1 = a_2$. Since $ g(f(a_1))=g(f(a_2))$ because $( g \circ f)(x)$ is one-to-one,$ a_1=a_2$. Thus $f(a_1)=f(a_2)$.Therefore, since $a_1=a_2$, $f$ is one-to-one. 
\end{enumerate}
\item Chapter 5.3 \# 2
\item Chapter 5.3 \# 6 Let $A = \mathbb{R}\setminus \{2\}$, and le $f$ be the function with domain $A$ defined by the formula $$f(x)=\frac{3x}{x-2}$$
\begin{enumerate}
\item Show that $f$ is  a one-to-one, onto function from $A$ to $B$ for some set $B \subseteq \mathbb{R}$. What is the set $B$. \\ 
One-to-one: According to the definition of $f$, we have\\  $$f(a_1)=f(a_2) $$ iff $$\frac{3a_1}{a_1 -2}=\frac{3a_2}{a_2 -2} $$
iff $$3a_1(a_2 -2)=3a_2(a_1 -2) $$
iff $$3a_1 a_2 - 6a_1 = 3a_1 a_2 2- 6 a_2 $$
iff $$-6a_1=-6a_2$$
iff $$a_1=a_2 $$
Thus there can be no real numbers $a_1$ and $a_2$ for which $f(a_1)=f(a_2)$ and $a_1 \not = a_2$. Thus $f$ is one-to-one.\\
Onto: Let $y$ be an arbitrary real number. Let $x= \frac{-2x}{3-y}$. Then $g(x)= \frac{3x}{x-2}=\frac{3\frac{-2y}{3-y}}{\frac{-2y}{3-y}-2}=\frac{\frac{-6y}{3-y}}{\frac{-2y-6+2y}{3-y}} = \frac{-6y}{-6}=y$. Thus $\forall y \in \mathbb{R} \exists x \in \mathbb{R} (g(x)=y)$.Therefore, $f$ is an arbitrary function. \\
The set $B= \mathbb{R} \setminus \{3\}$.\\
It has been shown that $f$ is one-to-one and unto from $A$ to $B$ for some set $B \subseteq \mathbb{R}$.
\item Find a formula for $f^{-1} (x)$.\\
$f^{-1} = \frac{2x}{x-3}$
\end{enumerate}
\end{enumerate}
\end{document}